Higgs Assisted Razor Search for Higgsinos at 100 TeV

### 2019-07-14 main.tex
Addressed all comments except one

% Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy
problem, it is under siege from recent data from the Large Hadron
Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
A compelling alternative scenario comes in the form of
split supersymmetry (split SUSY) \citep{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the
scale of 1-10 TeV, while the scalar superpartners can be much heavier,
on the scale of 100 - 1000 TeV. In exchange for accepting some level of
fine-tuning, we obtain numerous benefits, including the suppression of
flavor-changing neutral currents and greater compatibility with data
from CP-violation experiments.  The low lying 
fermionic superpartners consist of neutralinos and charginos (collectively
known as electroweakinos), and gluinos. The current LHC search limits on
gluinos are already around 2.4 TeV~\cite{CMS-PAS-SUS-19-005}. \Adarsh{Should
2460 GeV be rounded up to 2.5 TeV or down to 2.4 TeV to be conservative? Also,
this limit is from the disappearing track search - does that apply for us?} The
limits on electroweakinos,
howeer, are still relatively weak: around xxx $-$ xxx GeV~\cite{}, depending on
the decay modes of the parent electroweakinos.  \Shufang{add ref for 
electroweakino limits. Fill in the number.} In this paper, we will
focus on the discovery potential of the neutralinos and charginos at the 100
TeV $pp$ collider.

@@

Since the Bino is the only supersymmetric particle lighter than the Higgsino in the mass hierarchy we consider, the neutral Higgsino will decay to a Bino and a neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%. 
Search for Higgsinos with intermediate gauge boson and  multi-lepton final states have been studied in Ref.~\cite{Gori:2014oua}. \Shufang{Add more details for that study.  Which channel, search resutls, etc.  This would be our comparison for our analyses.}  In this paper we attempt to exploit the relatively high branching ratio of 
the SM Higgs boson to \emph{b} quarks, and study the decay mode $\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.

@@

The optimal search strategy for finding electroweakinos is highly dependent on
the their mass spectrums \citep{Han:2013kza}.  Phenomenological collider studies on finding
Electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
found in \citep{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
\Shufang{Say a few words about typical search strategy there.} \Adarsh{I
believe I've already addressed this with the paragraphs I added below in response
to your comment ... let me know if I should add more details.}.
Well-separated spectra have been studied in \citep{Gori:2014oua,
Acharya:2014pua} using
multi-lepton channels, of the form 
\begin{equation}
pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
\widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2l/3l +  
\met,
\end{equation}
\noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, and
$\widetilde{\chi}_1^0$ is the lightest neutralino. These searches work well since
the large mass difference between the Electroweakinos can lead to energetic
leptons that can be easily identified. Among the multi-lepton searches for
Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$ have the best reach, due to the relatively high production cross-section of
chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
and QCD backgrounds obtained by requiring three leptons.   The cross sections for trilepton process can be find in Table~\ref{tab:xsections}. Multilepton searches
with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
due to the lower pair-production cross-section of neutral Higgsinos, combined
with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
multilepton searches, the channel with \emph{Zh} (originally suggested in
\citep{Han:2013kza}) as the intermediate dibosons emerges as a possible
competitor to the \emph{WZ} channel.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/higgsino_production_xsection.png}
  \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
  \caption{Higgsino pair production cross section, as a function of $|\mu|$. The
  cross-sections are calculated using Prospino2, with $M_1 = 25$ GeV. However, it
  should be noted that the dependence on $M_1$ is very weak.  \Shufang{Could you make the two plot same aspect ratios?}}
  \label{fig:xsection_plot}
\end{figure}

@@

The most stringent limits are obtained by ATLAS in \cite{Aaboud:2018htj},
where Higgsinos with masses between 130 and 230 GeV and between 290 and 880 
GeV are excluded using a search channel with a final state containing 3+ 
\emph{b}-jets. \Shufang{you mean more than 3 b jets?} The CMS analysis
in \cite{Sirunyan:2017ubx} which uses a combination of channels and final states 
$4b+\slashed{E}_T, 2l + 2j + \slashed{E}_T, 3l/4l + \slashed{E}_T$ and $2\gamma+\slashed{E}_T$ 
to exclude Higgsino-like neutralino masses up to 650-750 GeV, depending on the assumed branching 
fraction of the neutralino decays. Finally, the $4l$ final state has been studied by ATLAS in \cite{Aaboud:2018zeb}
to set a lower bound of 295 GeV on the Higgsino mass  \cite{Aaboud:2018zeb}.
\Shufang{So the only available limit is with gravitino LSP?  Then it does not apply.}
\Shufang{There is no  WZ+MET limit on Higgsinos NLSP?}

@@

We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
\texttt{MadEvent} \citep{Alwall:2014hca}, then passed those events to Pythia 6
\citep{Sjostrand:2006za} for showering and hadronization. Finally, we used
\texttt{Delphes 3} \citep{deFavereau:2013fsa} to perform a fast, parametrized
detector simulation, with the detector card devised by the FCC-hh working
group\footnote{\url{https://github.com/HEP-FCC/FCCSW/blob/master/Sim/SimDelphesInterface/data/FCChh_DelphesCard_Baseline_v01.tcl}}.
For the backgrounds, we allowed up to one additional jet in the final state, to
approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
parameter set to 40 GeV. The Higgsino pair production cross sections were
calculated using \texttt{Prospino2} \citep{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
Wino, we set its mass parameter $M_2$ to 3 TeV.  \Shufang{5 TeV was used for another calculation earlier.  Be consistent here.}

@@

\begin{enumerate}
  \tightlist
  \item \emph{Trigger}: Events were selected if they had at least one lepton
    with $p_{T}^\ell >$ 100 GeV.  \Shufang{This is quite a high trigger level cut.  Is the 100 TeV lepton trigger need such a high pT? or it is a lower pT trigger, with a 100 GeV advanced cut to suppress the bg?}

@@

  \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
\begin{align}
M_R &=& \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)^2
- \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
\end{align}
 for$E_{Z,h}$ and $p_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$.
\Shufang{Check the formula.  Unit is not correct.}
    Representative kinematic
  distributions of these variables for signal events of a 1 TeV Higgsino and a 25 GeV Bino, as well as $tt$ and $tbW$ backgrounds are
  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification, and
  $\slashed{E}_{T}$ cuts. The
  distribution for the \emph{bbWW} background is not shown, since it is negligible in
  comparison to the others.   We can see that the distribution of $M_R$ is peaked
  around 1 TeV for the signal, which consistent with what we would expect, since
  it corresponds to the mass difference between the NLSP and LSP.  For this mass combination, requiring $M_R >$ 800
  GeV and $M_T^R >$ 400 GeV yields the greatest significance.

@@

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with a $|\mu| =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are averages \Shufang{What do you mean by average?}  of the cross-sections output by
MadEvent after performing the MLM matching procedure. Their small size reflects
the $m_{\ell\ell}$ and $\slashed{E}_T$ cuts we imposed at the parton level. For all
the benchmark points, we require a minimum of 5 signal events left over after
cuts. We can see that, after applying our cuts, $tt$ and $tbW$ remain as the
dominant backgrounds. The values of the razor variable cuts were chosen to
maximize the significance, $S/\sqrt{B}$ (calculated for an integrated luminosity
of 3000 fb$^{-1}$), shown in the last column.  \Shufang{For the reach plot, does razor variable cut value changes for each grid point?}

@@

For each signal mass combination and each background process, we preselected
events that passed the lepton trigger, contained two SFOS leptons and two
$b$-tagged jets, and calculated a number of kinematic variables for each event. We then
placed these kinematic variables in an array, with each row corresponding to an event, and
the columns corresponding to the kinematic variables. A mixture of low-level and high level
kinematic variables was shown to have the greatest effectiveness. The kinematic variables chosen were
$m_{\ell\ell}$, $m_{bb}$, $M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic
transverse energy $THT$, \Shufang{THT?} and transverse momenta of individual final state
leptons and $b$-quarks: $p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We
then divided the events into training and test sets, with the training set
comprising 75\% of signal events and 30\% of background events. \Shufang{You mean 70\% of all signal event generated? } We used the
\texttt{scikit-learn} package  \citep{Pedregosa2011} to implement our analysis.
{\it A boosted decision tree classifier was trained with 1000 weak learners and a
learning rate of 0.025. } \Shufang{We probably don't need this details.}  After the classifier is trained, we use it to assign
scores to individual events. A more negative score indicates a more
background-like event, and a more positive score denotes a more signal-like
event. After the scores have been assigned to the events in the test sets, we
can use this score just as we would a regular kinematical variable, that is, we
apply a cut that selects events with a minimum of this score. The value of the
cut is chosen to maximize the significance for each signal benchmark point. The
distribution of scores for the specific benchmark point ($|\mu|$ = 1 TeV, $M_1$
= 25 GeV) is shown in figure \ref{fig:bdt_response}. We observe that there is an
appreciable separation between the signal and background distributions.

@@

Table \ref{tab:bdt_cutflowtable} shows the cut efficiences for the same
representative benchmark point as in table \ref{tab:cc_cutflowtable}, but this
time for a boosted decision tree analysis. We observe that the statistical
significance we can achieve goes up from 2.4 to 8.4, a roughly four-fold
increase.  \Shufang{Do we still require 5 signal events minimum here?}

@@

\caption{ Discovery (red) and exclusion (blue) contours for the traditional
  cut-and-count analysis (solid) and boosted decision tree analysis (dashed),
  for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$. \Shufang{Shall we show the lepton search result in this figure for comparison?} }

@@

Fig.~\ref{fig:contours} shows the expected reach in parameter space for
95\% C.L. exclusion and 5$\sigma$ discovery in the parameter space of $|\mu|$ vs. $M_1$ for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$. The cut-and-count strategy is able to discover
Higgsinos up to 750 GeV  and exclude them up to 1.3 TeV. \Shufang{How do you read out the numbers?}  The boosted decision
tree analysis, improves this reach - it is able to discover Higgsinos up to 1.3
TeV, and exclude them up to 1.8 TeV in favorable points in parameter space.
Similarly, Binos can be discovered up to 300 GeV and excluded up to 800 GeV with
the rectangular cut analysis, and the BDT analysis can discover them up to about
900 GeV and exclude them up to 1.3 TeV. Table \ref{tab:summary} contains a
summary of these results. Since the background left after cut is relatively low, We do not include systematic errors in these
estimates.

@@

In regions with large mass differences between the LSP and NLSP, the reach is
not as good, since the intermediate SM Higgs boson will be highly boosted, and
thus decay into a highly collimated pair of $b$-jets. The extent to which this
affects our results can be estimated from table \ref{tab:cc_cutflowtable}. We
see that requiring two $b$-tagged jets reduces our signal cross-section by
roughly 87\%. This is far more than the 28\% reduction that one might naively
expect as a result of applying the $b$-tagging efficiency of about 85\%
specified in our \texttt{Delphes} card.  \Shufang{How do you get the 28\% number? }

\begin{table}[h]
\centering
\begin{tabular}{l|rr}
\toprule
Analysis type & 5$\sigma$ (discovery)& 1.96$\sigma$ (exclusion)\\
\midrule
Rectangular cuts & (0.75, 0.30) & (1.3, 0.8)\\
BDT Analysis & (1.3, 0.90) & (1.8, 1.3)\\
\bottomrule
\end{tabular}
\caption{Discovery reaches and expected exclusion limits (in TeV) for the
parameters $(|\mu|,M_1)$ for the rectangular cuts and BDT analyses. \Shufang{Probably don't need this table.} }
\label{tab:summary}
\end{table}

@@

Overall, we find that the reach of our analysis strategy is a significant
improvement over that of the LHC.  \Shufang{Did we mention the LHC reach?}  We found that the rectangular cut strategy has
the potential to discover Higgsino LSPs up to a mass of 750 GeV, and exclude
them up to a mass of 1.3 TeV. As expected, the boosted decision tree classifier
performs better, with the ability to discover Higgsino NLSPs up to 1.3 TeV and
exclude them up to a mass of 1.8 TeV. With the BDT analysis, Bino dark matter
candidates can be discovered up to 900 GeV, and excluded up to 1.3 TeV. In the
process, we highlighted the importance of generating enough Monte Carlo events
to estimate the huge backgrounds at a 100 TeV $pp$ collider.

>>>>

% Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy
problem, it is under siege from recent data from the Large Hadron
Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
A compelling alternative scenario comes in the form of
split supersymmetry (split SUSY) \citep{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the
scale of 1-10 TeV, while the scalar superpartners can be much heavier,
on the scale of 100 - 1000 TeV. In exchange for accepting some level of
fine-tuning, we obtain numerous benefits, including the suppression of
flavor-changing neutral currents and greater compatibility with data
from CP-violation experiments.  The low lying 
fermionic superpartners consist of neutralinos and charginos (collectively
known as electroweakinos), and gluinos. The current LHC search limits on
gluinos are already around 2.4 TeV~\cite{CMS-PAS-SUS-19-005}. \Adarsh{Should
2460 GeV be rounded up to 2.5 TeV or down to 2.4 TeV to be conservative? Also,
this limit is from the disappearing track search - does that apply for us?} The
limits on electroweakinos,
howeer, are still relatively weak: around 0.3 $-$ 1.1 \Adarsh{I'm rounding 1150
GeV down to 1.1 TeV - is that ok?}
TeV~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae} \Adarsh{0.15
- 1.1 if we include the gravitino analysis}, depending on
the decay modes of the parent electroweakinos.  \Shufang{add ref for 
electroweakino limits. Fill in the number.} In this paper, we will
focus on the discovery potential of the neutralinos and charginos at the 100
TeV $pp$ collider.

@@

Since the Bino is the only supersymmetric particle lighter than the Higgsino in
the mass hierarchy we consider, the neutral Higgsino will decay to a Bino and a
neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%.  Searches for
Higgsinos with intermediate gauge boson and multi-lepton final states have been
studied in Ref.~\cite{Gori:2014oua}. \Shufang{Add more details for that study.
Which channel, search resutls, etc. This would be our comparison for our
analyses.} \Adarsh{These details are already in section 2 (page 3) - should I
repeat them here?}  In this paper we attempt to exploit the relatively high branching
ratio of the SM Higgs boson to \emph{b} quarks, and study the decay mode
$\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.

@@

The optimal search strategy for finding electroweakinos is highly dependent on
the their mass spectrums \citep{Han:2013kza}.  Phenomenological collider studies on finding
Electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
found in \citep{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
\Shufang{Say a few words about typical search strategy there.} \Adarsh{I
believe I've already addressed this with the paragraphs I added below in response
to your comment ... let me know if I should add more details.}.
Well-separated spectra have been studied in \citep{Gori:2014oua,
Acharya:2014pua} using
multi-lepton channels, of the form

\begin{align}
  pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
  \widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2l/3l +  
  \met,
\end{align}

\noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, and
$\widetilde{\chi}_1^0$ is the lightest neutralino. These searches work well since
the large mass difference between the Electroweakinos can lead to energetic
leptons that can be easily identified. Among the multi-lepton searches for
Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$ have the best reach, due to the relatively high production cross-section of
chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
and QCD backgrounds obtained by requiring three leptons.   The cross sections for trilepton process can be find in Table~\ref{tab:xsections}. Multilepton searches
with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
due to the lower pair-production cross-section of neutral Higgsinos, combined
with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
multilepton searches, the channel with \emph{Zh} (originally suggested in
\citep{Han:2013kza}) as the intermediate dibosons emerges as a possible
competitor to the \emph{WZ} channel.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/higgsino_production_xsection.png}
  \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
  \caption{Higgsino pair production cross section, as a function of $|\mu|$. The
  cross-sections are calculated using Prospino2, with $M_1 = 25$ GeV. However, it
  should be noted that the dependence on $M_1$ is very weak.  
  \Shufang{Could you make the two plot same aspect ratios?}}
  \Adarsh{It would be pretty time consuming to do, so I would rather not if
    it's not essential - I think it might look better to put the plots in
  separate figures.}
  \label{fig:xsection_plot}
\end{figure}

@@

The most stringent limits are obtained by ATLAS in \cite{Aaboud:2018htj},
where Higgsinos with masses between 130 and 230 GeV and between 290 and 880 
GeV are excluded using a search channel with a final state containing at least
three \emph{b}-jets. \Shufang{you mean more than 3 b jets?} \Adarsh{At least 3 -
I've reworded to clarify.} The CMS analysis
in \cite{Sirunyan:2017ubx} which uses a combination of channels and final states 
$4b+\slashed{E}_T, 2l + 2j + \slashed{E}_T, 3l/4l + \slashed{E}_T$ and $2\gamma+\slashed{E}_T$ 
to exclude Higgsino-like neutralino masses up to 650-750 GeV, depending on the assumed branching 
fraction of the neutralino decays. Finally, the $4l$ final state has been studied by ATLAS in \cite{Aaboud:2018zeb}
to set a lower bound of 295 GeV on the Higgsino mass  \cite{Aaboud:2018zeb}.
\Shufang{So the only available limit is with gravitino LSP?  Then it does not apply.}
\Shufang{There is no  WZ+MET limit on Higgsinos NLSP?} \Adarsh{Yes, that is the
only available limit with neutral Higgsino NLSPs and bino LSP, and with
on-shell W and Z. WZ+MET limits (with on-shell W and Z). Should I remove the
sentences with the gravitino LSP?}.

@@

We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
\texttt{MadEvent} \citep{Alwall:2014hca}, then passed those events to Pythia 6
\citep{Sjostrand:2006za} for showering and hadronization. Finally, we used
\texttt{Delphes 3} \citep{deFavereau:2013fsa} to perform a fast, parametrized
detector simulation, with the detector card devised by the FCC-hh working
group\footnote{\url{https://github.com/HEP-FCC/FCCSW/blob/master/Sim/SimDelphesInterface/data/FCChh_DelphesCard_Baseline_v01.tcl}}.
For the backgrounds, we allowed up to one additional jet in the final state, to
approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
parameter set to 40 GeV. The Higgsino pair production cross sections were
calculated using \texttt{Prospino2} \citep{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
Wino, we set its mass parameter $M_2$ to 5 TeV. \Shufang{5 TeV was used for
another calculation earlier. Be consistent here.}

@@

\begin{enumerate}
  \tightlist
  \item \emph{Trigger}: Events were selected if they had at least one lepton
    with $p_{T}^\ell >$ 100 GeV.  \Shufang{This is quite a high trigger level
    cut.  Is the 100 TeV lepton trigger need such a high pT? or it is a lower
  pT trigger, with a 100 GeV advanced cut to suppress the bg?} \Adarsh{I had it
at 20 GeV earlier, but Ken Johns (and maybe you?) told me that that would be
far too low for a 100 TeV collider. Also, this is consistent with the analysis
in \cite{Gori:2014oua}.}

@@

  \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
\begin{align}
M_R &=& \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)
- \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
\end{align}
 for$E_{Z,h}$ and $p_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$.
 \Shufang{Check the formula.  Unit is not correct.} \Adarsh{Fixed.}
    Representative kinematic
  distributions of these variables for signal events of a 1 TeV Higgsino and a 25 GeV Bino, as well as $tt$ and $tbW$ backgrounds are
  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification, and
  $\slashed{E}_{T}$ cuts. The
  distribution for the \emph{bbWW} background is not shown, since it is negligible in
  comparison to the others.   We can see that the distribution of $M_R$ is peaked
  around 1 TeV for the signal, which consistent with what we would expect, since
  it corresponds to the mass difference between the NLSP and LSP.  For this mass combination, requiring $M_R >$ 800
  GeV and $M_T^R >$ 400 GeV yields the greatest significance.

@@

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with a $|\mu| =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are \Shufang{What do you mean by average?}
\Adarsh{I reworded it.}
\ap{obtained from} MadEvent after performing the MLM matching procedure. Their small size reflects
the $m_{\ell\ell}$ and $\slashed{E}_T$ cuts we imposed at the parton level. For all
the benchmark points, we require a minimum of 3 signal events left over after
cuts. We can see that, after applying our cuts, $tt$ and $tbW$ remain as the
dominant backgrounds. The values of the razor variable cuts were chosen to
maximize the significance, $S/\sqrt{B}$ (calculated for an integrated luminosity
of 3000 fb$^{-1}$), shown in the last column.  \Shufang{For the reach plot,
does razor variable cut value changes for each grid point?} \Adarsh{Yes, for
the rectangular cuts analysis.}

@@

For each signal mass combination and each background process, we preselected
events that passed the lepton trigger, contained two SFOS leptons and two
$b$-tagged jets, and calculated a number of kinematic variables for each event. We then
placed these kinematic variables in an array, with each row corresponding to an event, and
the columns corresponding to the kinematic variables. A mixture of low-level and high level
kinematic variables was shown to have the greatest effectiveness. The kinematic variables chosen were
$m_{\ell\ell}$, $m_{bb}$, $M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic
transverse energy $THT$, \Shufang{THT?} \Adarsh{Should I use some different
notation? Maybe $H_T$?} and transverse momenta of individual final state
leptons and $b$-quarks: $p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We
then divided the events into training and test sets, with the training set
comprising 75\% of signal events and 30\% of background events. \Shufang{You
mean 70\% of all signal event generated?} \Adarsh{Yes.} We used the
\texttt{scikit-learn} package  \citep{Pedregosa2011} to implement our analysis.
A boosted decision tree classifier was trained with 1000 weak learners and a
learning rate of 0.025. \Shufang{We probably don't need this details.}
\Adarsh{I would like to keep it, for the sake of reproducibility (and for
future researchers to compare their ML-based methods to ours).}
After the classifier is trained, we use it to assign
scores to individual events. A more negative score indicates a more
background-like event, and a more positive score denotes a more signal-like
event. After the scores have been assigned to the events in the test sets, we
can use this score just as we would a regular kinematical variable, that is, we
apply a cut that selects events with a minimum of this score. The value of the
cut is chosen to maximize the significance for each signal benchmark point. The
distribution of scores for the specific benchmark point ($|\mu|$ = 1 TeV, $M_1$
= 25 GeV) is shown in figure \ref{fig:bdt_response}. We observe that there is an
appreciable separation between the signal and background distributions.

@@

Table \ref{tab:bdt_cutflowtable} shows the cut efficiences for the same
representative benchmark point as in table \ref{tab:cc_cutflowtable}, but this
time for a boosted decision tree analysis. We observe that the statistical
significance we can achieve goes up from 2.4 to 8.4, a roughly four-fold
increase.  \Shufang{Do we still require 5 signal events minimum here?}
\Adarsh{Actually, we do a minimum of three events - more consistent with
Poisson statistics. I've updated the previous mention of 5 events.}

@@

\caption{ Discovery (red) and exclusion (blue) contours for the traditional
  cut-and-count analysis (solid) and boosted decision tree analysis (dashed),
  for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$.
\Shufang{Shall we show the lepton search result in this figure for comparison?}
\Adarsh{You mean the results from \cite{Gori:2014oua}? That sounds pretty
difficult to do...}
}

@@

Fig.~\ref{fig:contours} shows the expected reach in parameter space for 95\%
C.L. exclusion and 5$\sigma$ discovery in the parameter space of $|\mu|$ vs.
$M_1$ for 100 TeV $pp$ collider with an integrated luminosity of 3000
fb$^{-1}$. The cut-and-count strategy is able to discover Higgsinos up to 750
GeV  and exclude them up to 1.3 TeV. \Shufang{How do you read out the numbers?}
\Adarsh{I am just looking at the plot and estimating the approximate boundaries
of the curves..}  The boosted decision tree analysis, improves this reach - it
is able to discover Higgsinos up to 1.3 TeV, and exclude them up to 1.8 TeV in
favorable points in parameter space.  Similarly, Binos can be discovered up to
300 GeV and excluded up to 800 GeV with the rectangular cut analysis, and the
BDT analysis can discover them up to about 900 GeV and exclude them up to 1.3
TeV. Since the background left after cut is relatively low, We do not include
systematic errors in these estimates.

@@

In regions with large mass differences between the LSP and NLSP, the reach is
not as good, since the intermediate SM Higgs boson will be highly boosted, and
thus decay into a highly collimated pair of $b$-jets. The extent to which this
affects our results can be estimated from table \ref{tab:cc_cutflowtable}. We
see that requiring two $b$-tagged jets reduces our signal cross-section by
roughly 87\%. This is far more than the 28\% reduction that one might naively
expect as a result of applying the $b$-tagging efficiency of about 85\%
specified in our \texttt{Delphes} card.  \Shufang{How do you get the 28\%
number? } \Adarsh{$(1 - 0.85^2)*100 = 27.75 \approx 28$.}

\Adarsh{I removed the table as you suggested.}

@@

Overall, we find that the reach of our analysis strategy is a significant
improvement over that of the LHC.  \Shufang{Did we mention the LHC reach?}
\Adarsh{I was referring to the reach for the gravitino LSP analysis - should I
remove that?}  We found that the rectangular cut strategy has
the potential to discover Higgsino LSPs up to a mass of 750 GeV, and exclude
them up to a mass of 1.3 TeV. As expected, the boosted decision tree classifier
performs better, with the ability to discover Higgsino NLSPs up to 1.3 TeV and
exclude them up to a mass of 1.8 TeV. With the BDT analysis, Bino dark matter
candidates can be discovered up to 900 GeV, and excluded up to 1.3 TeV. In the
process, we highlighted the importance of generating enough Monte Carlo events
to estimate the huge backgrounds at a 100 TeV $pp$ collider.
